Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
todos and conclusion

\paragraph{Operators}
We need introduce operators for building expressions, of both action
and data sorts, when encoding the 
algebra into pNets. So that is needed to know about the input and
output of the operators used in the expressions from those
algebra. The input and output should belong to the sorts on the
pNet. When there are $k$ sorts in this pNet, the structure of a
$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
\TODO{ I do not understand this. As discussed today, I will wait till
  you include an example of algebra presentation before rewriting the comment.}

@@

\TODO{give an example of user-defined sorts/operators, and tell that
  you will give it's translation into Z3 in section 5.4}

@@

The assignments are also taken into account when checking the
satisfiability of the open transitions as they represent the value of
the variables involved in an OT. In order to do that, we employs a
translation from assignments into term of predicates. The assignments
required to be translated are only those belong to the variables
contain in the start states of the open transitions. The assignments
are represented as equations between the variables and the expressions
on the right side of assignment. For the assignments of the same
variable, we do not figure out which state is the precursor of current
state, we keep all these possible equations instead, and generate the
disjunction of these equations. The state could always move to the
target state if there exists one of the values of its variable
satisfies the guard.
\TODO{It won't matter the variable of the next state
except that the right hand side expression contain its variables. This
is a problem left to be solved in our future work. WHICH PROBLEM ?}
After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.

@@

\TODO{Conclusion: what you have accomplished, clearly state your
  contributions, and what is delivered at the end of your internship
  work}
\QIN{
In this paper we presented the algorithm of generating the open automaton for the open pNet involving the implementation part of the algorithm. Our implementation includes two main parts. First, we compute all the possible open transitions. The actions in pLTS and hole behaviors are composed in the algorithm while the generation of predicate need to match the combinations of the subnets with the synchronization vectors. Then we ensure the correctness of the intermediate result. The method use a SMT solver Z3 for checking the satisfiability of the open transitions using the predicate of them. In order to do that, we have done some translation on the presentation, the predicate and the assignments of the variables which are also considered as a part of predicates before submitting them to the Z3. We implemented our algorithm in the VerCors platform and use some running examples, the formula from other process algebras, to test the algorithm. The result of the running examples are shown as the open automaton with all the parameters generated by the algorithm automatically. The open automaton successfully presents all the possible movement of the formula. 
}

>>>>

\paragraph{Operators}
We need introduce operators for building expressions, of both action
and data sorts, when encoding the 
algebra into pNets. So that is needed to know about the input and
output of the operators used in the expressions from those
algebra. The input and output should belong to the sorts on the
pNet. When there are $k$ subnets in this pNet, the structure of a
$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.

@@

%\TODO{give an example of user-defined sorts/operators, and tell that
%  you will give it's translation into Z3 in section 5.4}

@@

The assignments are also taken into account when checking the
satisfiability of the open transitions as they represent the value of
the variables involved in an OT. In order to do that, we employs a
translation from assignments into term of predicates. The assignments
required to be translated are only those belong to the variables
contain in the start states of the open transitions. The assignments
are represented as equations between the variables and the expressions
on the right side of assignment. For the assignments of the same
variable, we do not figure out which state is the precursor of current
state, we keep all these possible equations instead, and generate the
disjunction of these equations. The state could always move to the
target state if there exists one of the values of its variable
satisfies the guard.
%\TODO{It won't matter the variable of the next state
%except that the right hand side expression contain its variables. This
%is a problem left to be solved in our future work. WHICH PROBLEM ?}
After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.

@@

In this paper we presented the algorithm for generating an open
automaton representing the semantics of an open pNet, and we described
the implementation of the
algorithm. Our implementation includes two main parts. First, we
compute all the possible open transitions. The actions in pLTS and
hole behaviors are composed in the algorithm while the generation of
predicate need to match the combinations of the subnets with the
synchronization vectors. Some of the open transitions obtained at this
intermediate step, constructed in a structural manner from all
possible combinations of possible logical predicates, may
contain predicates which do not represent any possible concrete
instanciations. 
To get rid of these useless transtions, we use a SMT solver Z3 for checking the
satisfiability of the predicate in each open transition. In
order to do that, we have done some translation on the presentation,
the predicate and the assignments of the variables which are also
considered as a part of predicates before submitting them to the
Z3 solver. We implemented our algorithm in the VerCors platform and use some
running examples, the formula from other process algebras, to test the
algorithm. The result of the running examples are shown as the open
automaton with all the parameters generated by the algorithm
automatically. The open automaton successfully presents all the
possible movement of the formula.
